---
title: "Running an OzFlux site budget"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running an OzFlux site budget}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

`render_site_budget()` renders a self-contained HTML report for one site's
completed simulation, comparing model outputs with observations and plotting
carbon, nitrogen, water, vegetation and soil diagnostics. The report template
and stylesheet are installed with `daveanalysis`. There is no separate report
to download, clone or edit. Render once per site.

The repository's `scripts/` directory is excluded from package builds, but the
report was moved to `inst/rmarkdown/site-budget/`. R installs the contents of
`inst/` into the package directory, so the template, stylesheet and output
manifest are all available after installation. For example, the template can
be located with:

```{r installed-template}
system.file("rmarkdown", "site-budget", "site_budget.rmd",
            package = "daveanalysis", mustWork = TRUE)
```

Neither helper requires a checkout of this analysis repository.

Examples are not executed when building this vignette because they require
simulation outputs.

## Requirements

1. Run an LPJ-GUESS/DAVE version that provides the diagnostic outputs listed
   below for each site of interest. Standard LPJ-GUESS outputs alone are not
   sufficient. Keep the daily and annual outputs from the same simulation.
2. Install `daveanalysis` and its dependencies, plus `rmarkdown`.
   Rendering HTML also requires Pandoc, available with RStudio or separately.
3. Supply the simulation repository root, site name and PFT name. The wrapper
   requires all three explicitly; it does not run the model or detect the PFT.
4. Standard observations, including EucFACE soil moisture, are installed with
   the package and registered when it loads. No observation path is needed.
   Supplementary AWRA observations are external and optional.

## Enable outputs before running the model

Use the installed helper to configure all required output files:

```{r enable-outputs}
library(daveanalysis)
repo <- "/path/to/simulation-repository"
enable_required_outputs(repo)
```

This edits `<repo>/benchmarks/ozflux/outputs.ins` in place. It enables the
98 common outputs plus both site-dependent soil-moisture outputs, and sets
`ifdailyoutput` to `1`. It uncomments existing settings, appends missing ones,
and replaces empty or custom output filenames with the filenames expected by
the report. Unrelated settings, `outputdirectory`, and trailing comments are
retained. Repeated calls make no further changes.

If a required setting has multiple active definitions or an unrecognised value
syntax, the helper reports an error before writing any changes. When there is
an active definition, commented alternatives are left alone; otherwise only
the first commented definition is enabled. The helper returns the absolute
path to `outputs.ins` invisibly.

**Next, run LPJ-GUESS for your sites**, then render the reports below. The helper
does not run the model or generate missing results. Your model version must
support the requested outputs, and the run's instructions must import this
`outputs.ins` without overriding its settings later. Imported instruction
files are not edited.

## Render a report

Keep your settings in a small R script:

```{r render-budget}
library(daveanalysis)

report <- render_site_budget(
  repo = "/path/to/simulation-repository",
  site = "CumberlandPlain",
  pft = "MRS",
  output_file = "reports/CumberlandPlain.html",
  source_id = "simulation_1",
  source_label = "My simulation",
  description = "Model revision, parameters and simulation period."
)
```

`output_file` is relative to your working directory, or it can be absolute.
Its parent directories are created if needed, and an existing report at that
path is overwritten. The default is `<site>-budget.html` in your working
directory. The function returns the absolute HTML path invisibly.

The wrapper checks the benchmark layout and all required output filenames
before rendering, listing missing files together. It does not check file
contents, PFT columns or observation coverage. The report is rendered from a
temporary copy of the installed template and stylesheet, so the package can
be installed in a read-only location. Temporary files are removed on success
or error. Observation-reader registrations, logging level and the ggplot theme
changed by the report are restored afterwards.

`source_id` identifies the simulation and `source_label` labels it in plots
(defaulting to `source_id`). `description` should record the model revision,
parameters and simulation period. The report includes its render parameters
and R session information for reproducibility.

Presentation settings go in `params`, for example:

```{r presentation}
render_site_budget(
  repo = "/path/to/simulation-repository", site = "Warra", pft = "MRS",
  params = list(fig_width = 16, dpi = 120),
  quiet = TRUE
)
```

The supported overrides and defaults are `aspect_ratio = 0.6`,
`image_fmt = "png"`, `fig_width = 20`, `dpi = 96`, `retina = 2`,
`fig_align = "center"` and `out_width = "100%"`.
Use the explicit function arguments for simulation settings; `params` accepts
only presentation settings. `quiet = TRUE` suppresses rendering progress.

For multiple sites, loop over site names:

```{r multiple-sites}
for (site in c("CumberlandPlain", "Warra")) {
  render_site_budget(
    repo = "/path/to/simulation-repository", site = site, pft = "MRS",
    output_file = file.path("reports", paste0(site, ".html")),
    description = "Model revision, parameters and simulation period."
  )
}
```

Each call uses a fresh render environment. The developer script
`scripts/generate_site_budgets` also calls this wrapper for batch rendering;
ordinary package users do not need that script.

## Simulation location

`repo` is the root passed to `defineSource(..., format = OZFLUX)`. The reader
expects this layout, where `out` is an example output directory:

```text
/path/to/simulation-repository/
  benchmarks/
    ozflux/
      outputs.ins
      CumberlandPlain/
        CumberlandPlain.ins
        gridlist.txt
        out/
          dave_lai.out
          ...
```

`benchmarks/ozflux/outputs.ins` must contain an `outputdirectory` setting, for
example `outputdirectory "out"`. The reader reads that file directly; it does
not resolve this setting through imported instruction files. It locates outputs
under `<repo>/benchmarks/ozflux/<site>/<outputdirectory>/`.
The site instruction file is used for site discovery; `gridlist.txt` supplies
coordinates, including for sites outside the package's standard site list.
Use one site's coordinates and the exact site-directory name.

The analysis does not need Git history or an executable to render completed
runs: a directory preserving this structure is sufficient. A bare directory of
`.out` files is not accepted by the report's current `repo` interface.

## Required model outputs

The following are the exact filename stems read by the active report chunks,
including names constructed in loops. Append `.out` to each stem. The reader
also supports `.out.gz`. Filenames must match these stems: the analysis does
not map arbitrary output filenames from LPJ-GUESS instruction settings.

The helper above enables the corresponding `file_<stem>` settings for you.
For reference, these settings look like:

```text
file_dave_lai "dave_lai.out"
file_dave_gpp "dave_gpp.out"
```

The model version must implement these settings. An unavailable diagnostic
requires a compatible model version or a change to the report; renaming a
standard output does not supply the missing diagnostic.

All of these outputs are required for the full current report, even where a
chunk reads a value that it subsequently does not use:

```text
dave_acmass_mort.out
dave_acpool.out
dave_aet.out
dave_agpp.out
dave_alpha_leaf.out
dave_alpha_root.out
dave_alpha_sap.out
dave_alpha_storage.out
dave_amort_age.out
dave_amort_greff.out
dave_ancohort.out
dave_anee.out
dave_anflux.out
dave_anpp.out
dave_anretranslocated.out
dave_anstorage_drawdown.out
dave_anuptake.out
dave_aresp.out
dave_cgrow_leaf.out
dave_cgrow_root.out
dave_cgrow_sap.out
dave_cgrow_storage.out
dave_clitter.out
dave_cmass_leaf.out
dave_cmass_leaf_limit.out
dave_cmass_repr.out
dave_cmass_root.out
dave_cmass_root_limit.out
dave_cmass_sap.out
dave_cmass_sap_limit.out
dave_cmass_standing_heart.out
dave_cmass_standing_leaf.out
dave_cmass_standing_repr.out
dave_cmass_standing_root.out
dave_cmass_standing_sap.out
dave_cmass_storage.out
dave_cmass_storage_limit.out
dave_cpool.out
dave_cton_leaf_max.out
dave_cton_leaf_min.out
dave_cton_root_max.out
dave_cton_root_min.out
dave_cton_sap_max.out
dave_cton_sap_min.out
dave_cturnover_leaf.out
dave_cturnover_root.out
dave_cturnover_sap.out
dave_cue.out
dave_density.out
dave_diameter.out
dave_dnpool.out
dave_fnuptake.out
dave_g1.out
dave_gpp.out
dave_height.out
dave_lai.out
dave_latosa.out
dave_ltor.out
dave_met_insol.out
dave_met_temp.out
dave_met_vpd.out
dave_ndemand.out
dave_nee.out
dave_nitrogen_budget_annual.out
dave_nitrogen_budget_daily.out
dave_nlitter.out
dave_nmass_leaf.out
dave_nmass_repr.out
dave_nmass_root.out
dave_nmass_sap.out
dave_nmass_storage.out
dave_nmass_storage_max.out
dave_npp.out
dave_nretranslocated.out
dave_nscal.out
dave_nstorage_drawdown.out
dave_nturnover_leaf.out
dave_nturnover_root.out
dave_nturnover_sap.out
dave_patch_ba.out
dave_resp.out
dave_resp_growth.out
dave_resp_leaf.out
dave_resp_maintenance.out
dave_resp_root.out
dave_resp_sap.out
dave_soil_psi_layer.out
dave_sompool_cmass.out
dave_sompool_decay_reduction.out
dave_sompool_nimmob.out
dave_sompool_nmass.out
dave_sompool_nmin_gross.out
dave_sw.out
dave_swvol.out
dave_water_budget_annual.out
dave_water_budget_daily.out
dave_weighted_psi.out
dave_wscal.out
```

There is one additional site-dependent output:

| Site | Additional required file |
| --- | --- |
| `CumberlandPlain` | `dave_swmm_100.out` |
| Any other site | `dave_swavail_100.out` |

`dave_aboveground_tree_biomass.out` is not required: its overview chunk is
commented out. `dave_height.out` is required by the active allometry chunk even
though its overview chunk is commented out. `dave_met_precip.out` appears only
in a commented test chunk and is not required.

### Required columns and simulation assumptions

Keep the native LPJ-GUESS headers and units, including `Lon`, `Lat`, `Year`,
and `Day` for daily outputs. Annual outputs use `Year`. Several calculations
join on these columns, and the nitrogen-usage chunk explicitly selects day 365.
The report mixes daily and annual diagnostics; annual files cannot replace
required daily files. Use overlapping simulation and observation dates.

The selected `pft` must be present in outputs read by PFT. Many other chunks
assume one resulting model series and do not pass `pft` to the reader; selecting
`pft` is not a report-wide filter for an arbitrary multi-PFT simulation.
The existing batch script describes single-PFT, single-cohort, single-patch
runs. Start with that setup; broader configurations need validation.

The report explicitly selects these non-PFT columns:

| Outputs | Columns |
| --- | --- |
| `dave_acpool`, `dave_cpool` | `VegC`, `StandingC`, `LitterC`, `SoilC`, `total` |
| `dave_dnpool` | `VegN`, `StandingN`, `LitterN`, `SoilN`, `AvailN` |
| `dave_clitter`, `dave_nlitter` | `SURFMETA`, `SURFSTRUCT`, `SURFCWD`, `SURFFWD` |
| All listed `dave_sompool_*` outputs | `SURFSTRUCT`, `SOILSTRUCT`, `SOILMICRO`, `SURFHUMUS`, `SURFMICRO`, `SURFMETA`, `SURFFWD`, `SURFCWD`, `SOILMETA`, `SLOWSOM`, `PASSIVESOM`, `total` |
| `dave_sw` | `sw_0` through `sw_14` |
| `dave_soil_psi_layer` | `soil_psi0` through `soil_psi14` |
| Both `dave_water_budget_*` outputs | `precip`, `evap`, `transp`, `interception`, `surfrunoff`, `drainrunoff`, `baserunoff`, `flux` |
| Both `dave_nitrogen_budget_*` outputs | `deposition`, `fixation`, `uptake`, `gross_mineralisation`, `immobilisation`, `net_mineralisation`, `min_leach`, `org_leach`, `volatilisation`, `gas_emissions`, `flux`, `flux_avail`, `avail`, `totaln` |
| `dave_anflux` | `MANUREN`, `NFERT`, `ESTN`, `HARVESTN`, `SEEDN`, `NH3_FIRE`, `NOx_FIRE`, `N2O_FIRE`, `N2_FIRE`, `NH3_SOIL`, `NO_SOIL`, `N2O_SOIL`, `N2_SOIL`, `NET_NITRIF`, `NET_DENITRIF`, `GROSS_NITRIF`, `GROSS_DENITRIF` |

The fire section additionally expects `total` in `dave_cmass_standing_leaf`.

## Observations

The package's `inst/data/` contains MODIS and TERN LAI, GOSIF GPP, flux-tower
precipitation, temperature, radiation, soil moisture, ET and carbon fluxes,
SMIPS soil moisture and ET, forest inventory measurements, and EucFACE soil
moisture. These are located through `system.file("data", package = "daveanalysis")`
and registered automatically by the package's observation-reader registry.
Users do not need to configure their location.

Bundled data do not guarantee observations for every site or date. The current
report explicitly renames `flux_nee`, `flux_gpp`, `flux_resp`, `gosif-gpp` and
`flux_rsds` columns. Missing observational series can therefore stop rendering;
the full report is not currently a general observation-free site budget.

### Optional AWRA observations

To add AWRA comparisons, pass `data_dir` as the root containing your `awra/`
subdirectory:

```{r supplementary-observations}
render_site_budget(
  repo = "/path/to/simulation-repository", site = "Warra", pft = "MRS",
  data_dir = "/path/to/supplementary-observations"
)
```

The wrapper checks that this subdirectory exists. Its contents must be the
AWRA CSV files expected by `register_supplementary_observations()`.
Leave `data_dir = NULL` (the default) to use registered observations without
adding AWRA readers. This does not trigger a missing-AWRA warning.
`data_dir` does not relocate the bundled observations. CumberlandPlain uses
the bundled EucFACE reader directly, with no machine-specific path.

## Updating and customising the workflow

Keep your render script outside the installed package. Updating `daveanalysis`
updates its report template while leaving your settings in your own script,
so there are no local report edits to merge. Record or pin the package version
alongside the model revision when you need reproducible results.

For maintainers, the canonical template is now
`inst/rmarkdown/site-budget/site_budget.rmd`, with its stylesheet and a
`required-outputs.txt` manifest beside it. The wrapper uses this manifest for
file validation, adding the site-dependent soil-moisture output. When report
chunks change, update the manifest and this vignette's output/column lists
together. The exported `enable_required_outputs()` helper uses the same manifest.
The old `scripts/enable_required_outputs -r <repo>` command remains as a thin
Rscript entry point calling that installed helper. The old
`scripts/site_budget.rmd` has moved; scripts that previously called `rmarkdown::render()` on it should call `render_site_budget()` instead.

Further improvements could validate output columns and observation coverage
before rendering, or offer optional sections with their own requirements.
The current wrapper retains the full report's scientific calculations and
site/PFT assumptions described above.
